Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-07 paper/paper.tex
formatted labels and edited cplx-gaussian section

  z \sim \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
$, with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation
matrices $\Gamma$ and $C$ are, respectively, if 

@@

$. This distribution possesses the usual properties of $\real$-valued Gaussians, including
if $y = A z + b$ for $
  A \in \cplx^{n \times m}
$ and $b \in \cplx^{n}$, then $

@@

$. The entropy of a $\cplx$-Gaussian distribution $
  q = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
$ is

@@

    = \tfrac12 \log \det{\biggl(
      2 \pi e \tfrac12
    \biggr)}

@@

    = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}

@@

A $\cplx$-Gaussian random vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated,
i.e. $C = 0$, since the matrices $\Gamma$ and $C$ correspond to $
$, respectively. From \eqref{eq:c-gauss-entropy-derivation} its entropy is therefore 

@@

\subsubsection{Variational dropout} % (fold){}
\label{ssub:variational_dropout}

>>>>

  z \sim q(z) = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
$, with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation matrices
$\Gamma$ and $C$, respectively, if

@@

$. Matrices $\Gamma$ and $C$ are $
$, respectively. $\cplx$-Gaussians are closed under affine transformations: if $y = A z + b$
for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$, then $

@@

$. The entropy of a $\cplx$-Gaussian distribution coincides with the entropy of
\eqref{eq:cn-paired-real-density}, and in terms of $\Gamma$ and $C$ can be expresed:

@@

    %   2 \pi e \tfrac12
    %     \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
    %     \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}

@@

    = \tfrac12 \log \det{(\pi e \Gamma)}
      \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}

@@

A $\cplx$-Gaussian vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated, i.e.
$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} the entropy of a proper $\cplx$-Gaussain is

@@

\subsubsection{Variational dropout} % (fold)
\label{ssub:variational_dropout}
